%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Support Technician} % Job title
    {Health Canada} % Organization
    {Ottawa, Ontario} % Location
    {Sep. 2019 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Provide support for key government departments during the COVID-19 pandemic.}
        \item {Utilize HP Service Manager to diagnose and solve employee account issues.}
        \item {Manage employee Open Enterprise Server, Active Directory, Outlook, etc. accounts.}
	    \item {Participate in initiatives to clean-up and streamline account management databases.}
	    \item {Follow Standard Operating Procedures to ensure uniformity within the team's tasks.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Front of House} % Job title
    {Nostimo Greek Souvlaki} % Organization
    {Aurora, Ontario} % Location
    {Apr. 2017 - Aug. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Took and handled payment for all orders, in-store, over the phone, and online.}
        \item {Served food and drink to customers in store.}
	\item {Assisted with food preparation and packing for to-go orders.}
        \item {Handled cleaning of front kitchen area, eating area, as well as washrooms.}
	\item {Directed logistics tasks for the restaurant such as updating online menus and enrolling in services such as UberEats.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Freelance IT Admin} % Job title
    {Fiverr} % Organization
    {Global} % Location
    {May. 2015 - Apr. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item {Provided IT consultation for 20+ clients across the world.}
	\item {Setup a multitude of services and programs on client servers/PC's.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
