%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurriculars \& Side Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  %---------------------------------------------------------
  \cventry
    {Sole Developer} % Affiliation/role
    {Proprietary Information Management Project} % Organization/group
    {Ottawa, Ontario} % Location
    {Dec. 2019 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
      \item {Currently developing an embedded system and accompanying smartphone app to simplify everyday life through the use of NFC.}
      \item {Developing the embedded system with C++, utilizing an Arduino microcontroller and PN532 NFC controller.}
      \item {Developing the Android app frontend with Kotlin, heavily depending on the Android Jetpack library suite.}
      \item {Utilizing Google Firebase to take advantage of a serverless architecture.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Participant} % Affiliation/role
    {CUHacking Coding Competition} % Organization/group
    {Ottawa, Ontario} % Location
    {Jan. 11-12, 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
      \item {Participated within a team to compete in the annual Carleton University hacking/coding competition.}
      \item {Created a JavaScript web app to analyze and visualize a provided JSON data set as part of the Martello Challenge.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Participant} % Affiliation/role
    {CUHacking Coding Competition} % Organization/group
    {Ottawa, Ontario} % Location
    {Feb. 16-17, 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
      \item {Participated within a partnership to compete in the annual Carleton University hacking/coding competition.}
      \item {Utilized Google Cloud Platform's Vision API to dynamically generate colour palettes with only keywords as input.}
      \end{cvitems}
    }

%---------------------------------------------------------
  % \cventry
  %   {Organizer on Tech Committee } % Affiliation/role
  %   {TEDxSacredHeartCHS} % Organization/group
  %   {Thornhill, Ontario} % Location
  %   {May. 2015 - Apr. 2016} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) of experience/contributions/knowledge
  %       \item {Worked with theater staff to coordinate technological aspects of the event.}
  %       \item {Assisted with design of event graphics as well as creation of event website.}
  %     \end{cvitems}
  %   }

%---------------------------------------------------------
\end{cventries}
